\chapter{Analysis}

\section{Introduction}

\subsection{Client Identification}
My client is Kathryn Roberts who owns Tots 2 Teens childcare services. The business provides childcare to people. They want a system developing as they want their current system computerizing.
\subsection{Define the current system}
The current system has a sheet of paper printed out at the beginning of the week with all the children's names on and when the child is dropped off and collected the time is recorded on the sheet. At the end of the week the sheet is taken home and the times are recorded into a excel invoice that calculates the price from the times that are recorded in it. at the end of the month the invoices are sent off to the parents.
\subsection{Describe the problems}
Some problems with the current system include some times do not get recorded due to human error. Some times can't be read due to poor handwriting. The sheet may not get printed out on time so times can't be recorded.
\subsection{Section appendix}

\section{Investigation}

\subsection{The current system}

\subsubsection{Data sources and destinations}

\subsubsection{Algorithms}

\subsubsection{Data flow diagram}

\subsubsection{Input Forms, Output Forms, Report Formats}

\subsection{The proposed system}

\subsubsection{Data sources and destinations}

\subsubsection{Data flow diagram}

\subsubsection{Data dictionary}

\subsubsection{Volumetrics}

\section{Objectives}

\subsection{General Objectives}

\subsection{Specific Objectives}

\subsection{Core Objectives}

\subsection{Other Objectives}

\section{ER Diagrams and Descriptions}

\subsection{ER Diagram}

\subsection{Entity Descriptions}

\section{Object Analysis}

\subsection{Object Listing}

\subsection{Relationship diagrams}

\subsection{Class definitions}

\section{Other Abstractions and Graphs}

\section{Constraints}

\subsection{Hardware}

\subsection{Software}

\subsection{Time}

\subsection{User Knowledge}

\subsection{Access restrictions}

\section{Limitations}

\subsection{Areas which will not be included in computerisation}

\subsection{Areas considered for future computerisation}

\section{Solutions}

\subsection{Alternative solutions}

\subsection{Justification of chosen solution}